A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-03 paper.tex
Minor edits

\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
 \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.  The fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
 \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.  By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.  The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
\end{itemize}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$. 
\end{theorem}

>>>>

\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $\Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
 \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
 \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.  By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.  The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
\end{itemize}

@@

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.  Moreover, this equivalence is $\mr U(1)$-equivariant.
\end{theorem}
